A general and efficient representation of Ancestral Recombination Graphs

### 2022-10-15 paper.tex
Fixed rates in ARG description

In the Griffiths formulation (the big ARG process), each edge in the graph corresponds to an extant
lineage and nodes are events in the process. The $n$ initial leaf nodes are
sampling events. Common ancestor events occur at rate $\binom{|L|}{2}$.
When a common ancestor event happens, two uniformly chosen lineages
merge into a common ancestor lineage.
Recombination events happen at rate $|L| \rho$. Here, we choose a lineage (i.e.\ edge) uniformly,
and a breakpoint $0 < x < m$ uniformly on its genome. We terminate the edge at a
node, record the breakpoint, and start two new edges from this node. The process
then continues until there is only one lineage left (the Grand Most Recent
Common Ancestor, GMRCA), which is guaranteed to
happen in finite time because of the linear rate of coalescing vs.\ quadratic rate of branching.

>>>>

In the Griffiths formulation (the big ARG process), each edge in the graph corresponds to an extant
lineage and nodes are events in the process. The $n$ initial leaf nodes are
sampling events. Common ancestor events occur at rate $\binom{|L|}{2}$.
When a common ancestor event happens, two uniformly chosen lineages
merge into a common ancestor lineage.
Recombination events happen at rate $|L| \rho$. Here, we choose a lineage (i.e.\ edge) uniformly,
and a breakpoint $0 < x < m$ uniformly on its genome. We terminate the edge at a
node, record the breakpoint, and start two new edges from this node. The process
then continues until there is only one lineage left (the Grand Most Recent
Common Ancestor, GMRCA), which is guaranteed to
happen in finite time because of the quadratic rate of coalescing vs.\ linear rate of branching.
